The Concurrent Calculi Formalisation Benchmark

### 2024-01-29 short-paper/short-paper.tex
Further copy-editing

\section{Introduction}
By establishing a common ground for systematically evaluating mechanisation techniques, 
the POPLMark challenge~\cite{POPLMark} accelerated progress in 
the development of proof assistants, libraries, and best practices. In doing so, it 
spearheaded a shift in the programming lanuage research community towards 
publications that include mechanised proofs. 
Its follow-up challenge, POPLMark Reloaded~\cite{POPLMarkReloaded}, 
facilitated the development of best practices and tool support for proofs 
using logical relations. These challenges were deliberately limited in scope, 
while their authors called for future investigations into such areas as 
coinduction and linear environments. In this spirit, we propose a 
new collection of benchmark problems specifically designed to address typical 
issues that arise when mechanising message-passing concurrency using process 
calculi.

Several papers in this realm already include mechanised proofs
(e.g.~\cite{Castro-Perez2021,Castro2020,lmcs:9985,
  DBLP:journals/jar/CruzFilipeMP23, Tirore:2023}), or discuss proof mechanisation techniques
(e.g.~\cite{Bengtson2016, Gay2001,
  Thiemann2019, DBLP:conf/forte/ZalakainD21}).  Our
experience, however, is that choosing the appropriate proof mechanisation techniques and 
tools remains a significant challenge with a limited understanding of their 
respective tradeoffs.  This often leads researchers toward a trial-and-error approach, 
resulting in sub-optimal and ad-hoc solutions. In turn, this increases the overall effort 
required for proof mechanisation, and hampers the reuse of techniques and results.
%
It is therefore our view that the research community in message-passing
concurrency (and process calculi, more specifically) will benefit from a standardised set
of challenge probems.

>>>>

\section{Introduction}
By establishing a common ground for systematically evaluating mechanisation techniques, 
the POPLMark challenge~\cite{POPLMark} accelerated progress in 
the development of proof assistants, libraries, and best practices. In doing so, it 
spearheaded a shift in the programming language research community towards 
publications that include mechanised proofs. 
Its follow-up challenge, POPLMark Reloaded~\cite{POPLMarkReloaded}, 
facilitated the development of best practices and tool support for proofs 
using logical relations. These challenges were deliberately limited in scope, 
while their authors called for future investigations into such areas as 
coinduction and linear environments. In this spirit, we propose a 
new collection of benchmark problems specifically designed to address typical 
issues that arise when mechanising message-passing concurrency using process 
calculi.

Several papers in this realm already include mechanised proofs
(e.g.~\cite{Castro-Perez2021,Castro2020,lmcs:9985,
  DBLP:journals/jar/CruzFilipeMP23, Tirore:2023}), or discuss proof mechanisation techniques
(e.g.~\cite{Bengtson2016, Gay2001,
  Thiemann2019, DBLP:conf/forte/ZalakainD21}).  Our
experience, however, is that choosing the appropriate proof mechanisation techniques and 
tools remains a significant challenge with a limited understanding of their 
respective tradeoffs.  This often leads researchers toward a trial-and-error approach, 
resulting in sub-optimal and ad-hoc solutions. In turn, this increases the overall effort 
required for proof mechanisation, and hampers the reuse of techniques and results.
%
It is therefore our view that the research community in message-passing
concurrency (and process calculi, more specifically) will benefit from a standardised set
of challenge problems.
